Verifying Demonstrations

### 2018-02-20 paper/ZKPK.tex
Adds Schnorr for PK protocol figure
Generalizes PK.{Prove,Verify}, SPK to generalized Schnorr

We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
    \prod_{i=1}^n g_i^{\alpha_i}}\).
This could equivalently be written as
\begin{equation*}
  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
  \PKverify[\{g_i\}_i, q, A],
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (1) or reject (0).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\PKprove[g, q, A, \alpha]\):
    &
    & \(\PKverify[g, q, A]\):
    \\

  \end{tabular}
  \caption{%
    \(\PK{\alpha}{A = g^\alpha}\) using the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}

@@

\begin{figure*}
  \begin{minipage}[t]{0.48\linewidth}
    \begin{algorithmic}
      \Function{$\SPKprove$}{$g, q, A, \alpha, m$}
        \State{$\rho\rgets \Z_q, R\gets g^\rho$}
        \State{$c \gets H(g|A|R|m)$}
        \State{$s \gets \rho - c\alpha$}
        \State{\Return{$(s, c)$}}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.48\linewidth}
    \begin{algorithmic}
      \Function{$\SPKverify$}{$g, q, A, m, s, c$}
        \State{$\hat R \gets g^s A^c$}
        \If{$c = H(g|A|\hat R|m)$}
          \State{\Return{1}}
        \Else{}
          \State{\Return{0}}
        \EndIf{}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \caption{%
    \(\SPK{\alpha}{A = g^\alpha}{m}\) using the Fiat-Shamir heuristic on the 
    Schnorr identification scheme.
  }%
  \label{SPKalgorithms}
\end{figure*}

>>>>

We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
    \prod_{i=1}^n g_i^{\alpha_i}}\).
This could equivalently be written as
\begin{equation*}
  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
  \PKverify[\{g_i\}_i, q, A],
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (1) or reject (0).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{equation*}
  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \PK{\alpha}{A = g^\alpha} 
  \land \PK{\beta}{B = g^\beta},
\end{equation*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \toprule

    \(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)
    &
    &
    \\

    \(R\gets \prod_{i=1}^n g_i^{\rho_i}\)
    & \(\ProtoSendRight{R}\)
    &
    \\

    % null
    & \(\ProtoSendLeft{c}\)
    & \(c\rgets \bin^k\)
    \\

    \(1\leq i\leq n\colon s_i\gets \rho_i - c\alpha_i \mod q\)
    & \(\ProtoSendRight{\{s_i\}_{i=1}^n}\)
    &
    \\

    % null
    &
    & \(R \stackrel{?}{=} A^c \prod_{i=1}^n g^{s_i}\)
    \\

    \bottomrule
  \end{tabular}
  \caption{%
    \(\PK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}\) using 
    the Schnorr identification scheme.
  }%
  \label{PKalgorithms}
\end{figure*}

@@

\begin{figure*}
  \begin{minipage}[t]{0.49\linewidth}
    \begin{algorithmic}
      \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
        \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)}
        \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
        \State{$c \gets H(\{g_i\}_i|A|R|m)$}
        \For{$1\leq i\leq n$}
          \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
        \EndFor{}
        \State{\Return{$(\{s_i\}_i, c)$}}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \begin{algorithmic}
      \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
        \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
        \If{$c = H(\{g_i\}_i|A|\hat R|m)$}
          \State{\Return{1}}
        \Else{}
          \State{\Return{0}}
        \EndIf{}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \caption{%
    \(\SPK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}{m}\) 
    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
  }%
  \label{SPKalgorithms}
\end{figure*}
